### 2010-11-17 articles/2009/geoinformatics/article.tex

Otto Dassau <dassau@nature-consult.de>: Otto lives and works in Hannover,
Germany. His topics are FOSS GIS and applied remote sensing.
\\Gary Sherman <gsherman@mrcc.com>: Gary lives and works in Alaska and been
torturing computers and programming languages well over two decades. In 2002
he founded the Quantum GIS project. 
\\Tim Sutton <tim@linfiniti.com>: Tim runs a consultancy business in
Gauteng, South africa where he provides commercial support and development
services for QGIS and other FOSS GIS software.
\\Marco Hugentobler <marco.hugentobler@karto.baug.ethz.ch>: Marco lives in
Zurich, Switzerland. He works for the Institute of Cartography, ETH Zurich
and for his company that provides programming and consulting services for
FOSS GIS software.
\\Paolo Cavallini <cavallini@faunalia.it>: Paolo lives and works in Italy. He
heads a small and active group of professionals (biologists and agronomists)
under the name Faunalia.

>>>>

Otto Dassau <dassau@nature-consult.de>: Otto lives and works in Hannover,
Germany. His topics are FOSS GIS and applied remote sensing.
\\Gary Sherman <gsherman@mrcc.com>: Gary lives and works in Alaska and been
torturing computers and programming languages well over two decades. In 2002
he founded the Quantum GIS project.
\\Tim Sutton <tim@linfiniti.com>: Tim runs a consultancy business in
Gauteng, South africa where he provides commercial support and development
services for QGIS and other FOSS GIS software.
\\Marco Hugentobler <marco.hugentobler@karto.baug.ethz.ch>: Marco lives in
Zurich, Switzerland. He works for the Institute of Cartography, ETH Zurich
and for his company that provides programming and consulting services for
FOSS GIS software.
\\Paolo Cavallini <cavallini@faunalia.it>: Paolo lives and works mostly in Italy. He
provides commercial support for QGIS and other FOSS GIS through his companies
Faunalia.it and Faunalia.pt, and promotes FOSS GIS through the non-profit
GFOSS.it.
